---
title: "HW0"
author: "Rachel Sussman"
execute:
  echo: false
---


## Exercises

(@) **Write a Quarto document that defines variables $a=1, b=-1, c=-2$
and print out the solutions to $f(x) = ax^2+bx+c=0$. Do not report complex solutions, only real numbers.**

```{r}
a=1
b=-1
c=-2

if(b^2 == 4*a*c){
  p1 = paste0("there is one solution. The solution is ", (-b + sqrt(b^2 - 4*a*c))/(2*a), ".")
  p2 = paste0("As indicated by the red dashed line, there is one point where the quadratic curve intersects with the line y=0, at x=", (-b + sqrt(b^2 - 4*a*c))/(2*a), ".")
}else if(b^2 > 4*a*c){
  p1 = paste0("there are two solutions. The solutions are ", (-b + sqrt(b^2 - 4*a*c))/(2*a), " and ", (-b - sqrt(b^2 - 4*a*c))/(2*a), ".")
  p2 = paste0("As indicated by the red dashed lines, there are two points where the quadratic curve intersects with the line y=0, one at x=", (-b + sqrt(b^2 - 4*a*c))/(2*a), " and the other at x=", (-b - sqrt(b^2 - 4*a*c))/(2*a), ".")
}else if(b^2 < 4*a*c){
  p1 = paste0("there are no real solutions.")
  p2 = paste0("As you can see, the quadratic curve does not intersect with the line y=0; hence, there are no solutions")
}
```

The quadratic formula can be applied to solve this equation: $$(-b \pm \sqrt{b^{2}-4ac})/2a $$

For the quadratic equation $`r a`x^{2} + `r b`x + `r c` = 0$, `r p1`

(@) **Include a graph of $f(x)$ versus $x$ for $x \in (-5,5)$.**

```{r}
x=seq(-5, 5, length.out = 300)
y=a*x^2 + b*x + c
plot(x, y, type = "l")
abline(h = 0, lty = 2)

if(b^2 == 4*a*c){
  abline(v = (-b + sqrt(b^2 - 4*a*c))/(2*a), col = "red", lty=2)
}else if(b^2 > 4*a*c){
    abline(v = (-b + sqrt(b^2 - 4*a*c))/(2*a), col = "red", lty=2)
    abline(v = (-b - sqrt(b^2 - 4*a*c))/(2*a), col = "red", lty=2)
}
```
Here is a graph of $f(x)$ versus $x$ for $x \in (-5,5)$. `r p2`

(@) **Generate a PDF report using knitr. Do not show the R code, only the solutions and explanations of what the reader is seeing.**

In the terminal, enter `quarto render HW0.qmd --to pdf`. Alternatively, in the RStudio console, enter `rmarkdown::render("HW0.qmd", "pdf_document")`. To hide the R code, type `execute: echo: false` in the Quarto file header or  `echo = FALSE` in each bracket that initializes a code chunk.

(@) **Erase the PDF report and reproduce it but this time using $a=1, b=2, c=5$.**

To erase the PDF report, enter `rm HW0.pdf` in the terminal. Then, to regenerate the PDF report using $a=1, b=2$, and $c=5$, assign 1, 2, and 5 to variables a, b, and c respectively on lines 15-17 of this Quarto file.

(@) **Erase the PDF report and reproduce it but this time using $a=1, b=3, c=2$.**

To erase the PDF report, enter `rm HW0.pdf` in the terminal. Then, to regenerate the PDF report using $a=1, b=3$, and $c=2$, assign 1, 3, and 2 to variables a, b, and c respectively on lines 15-17 on this Quarto file.

(@) **Create an HTML page with the results for this last set of values, but this time showing the code.**
 
To show the R code, either type `execute: echo: true` (or delete `execute: echo: false`) in the header or type `echo = TRUE` (or delete `echo = FALSE`) in each bracket that initializes a code chunk. Then, in the terminal, enter `quarto render HW0.qmd --to html`, or in the RStudio console, enter `rmarkdown::render("HW0.qmd", "html_document")`.